Precision calculations of the cosmic shear power spectrum projection

### 2017-02-05 limber2.tex
added some CFHTLenS results

@@

  \begin{tabular}{lc} \hline
  ID       & $\sigma_8 (\Omega_{\rm m}/0.3)^{0.6}$ \\ \hline
  L1Fl     & $0.769 \pm 0.031$ \\
  ExtL2Sph & $0.769 \pm 0.030$ \\ \hline
  \end{tabular}

>>>>

We run various projection modes on CFHTLenS single-redshift bin data
\cite{CFHTLenS-2pt-notomo}. The setting is exactly the same as for the 2013
results. Note that since then many improvements have been obtained, those
results do not reflect the most up-to-date cosmological constraints. This is
sufficient however for our purpose to show the effect of projection
approximations for weak-lensing surveys. Thos improvement have been made on the
theoretical modelling side (revised non-linear power spectrum
\cite{2012ApJ...761..152T}, baryonic modifications of the total power spectrum
\cite{2015MNRAS.454.1958M}), and the data processing (photometric redshifts
\cite{2016MNRAS.463.3737C,joudaki/etal:2016}, shear calibration
\cite{KiDS-450}, Fenech Compti). The state-of-the-art cosmological constraints
for CFHTLenS including most of those updates are presented in
\cite{joudaki/etal:2016}.

The mean and 68\% credible interval for $\sigma_8 (\Omega_{\rm m}/0.3)^{0.6}$
published in \cite{CFHTLenS-2pt-notomo} were $0.787 \pm 0.032$. We make sure
that changes introduced to \texttt{CosmoPMC} over the last four years do not
change this result, we re-run the same setting using the newest version of
\texttt{CosmoPMC} and obtain $0.787^{+0.031}_{-0.033}$.

Table \ref{tab:CFHTLenS_Sigma8} lists the mean and 68\% credible interval for
$\sigma_8 (\Omega_{\rm m}/0.3)^{0.6}$ for various approximations to the lensing
power spectrum projections.

As an example of significant effects that need to be accounted for, using the
revised non-linear power spectrum of \cite{2012ApJ...761..152T} instead of
\cite{2003MNRAS.341.1311S} yields $\sigma_8 (\Omega_{\rm m}/0.3)^{0.6} =
0.768^{+0.029}_{-0.031}$ for L1Fl, which is a lower corresponding to 60\% of
the error bar.

@@

  \label{tab:CFHTLenS_Sigma8}

  \caption{Mean and 68\% credible interval for 
  $\sigma_8 (\Omega_{\rm m}/0.3)^{0.6}$ for various approximations to the lensing
  power spectrum projections.}

  \begin{tabular}{lc} \hline
  ID       & $\sigma_8 (\Omega_{\rm m}/0.3)^{0.6}$ \\ \hline
  L1Fl     & $0.787^{+0.031}_{-0.033}$ \\
  ExtL2Sph & $0.788 \pm 0.032$ \\ \hline
  \end{tabular}
